Updates on the Exoplanet Orbit Database

### 2014-02-03 draft/ms.tex
Test
Added descriptions for KOI, EOD, and etc

@@

KOI

@@

EOD: Planets discovered by radial velocity and transit method are
classified as EOD planets. They have robust orbital parameters such as
PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
  describe why we include a planet in EOD -- this is covered at the
  beginning of Section~\ref{sec:update} as we discuss the `scope of
  EOD'. Just say what this flag is. Also, right now it includes RV,
  Transit, and also some Timing planets. The first sentence sounds
  like as long as a planet is discovered via RV and transit, it'll be
  in EOD, which is not true, I think.)}

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
methods other than radial velocity and transit. These planets are
categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.)}

@@

DIST: actually, DIST is not added since Wright 2011 (It was just left out)

@@

@@

DISCMETH - replaced by planetdiscmeth and stardiscmeth;

>>>>

TEST!

@@

KOI: KOI represents `Kepler Objects of Interest', which are planet candidates that have not been confirmed.

@@

EOD: EOD flag indicates planets with good Keplerian orbits. They have robust orbital parameters such as PER, ECC, K, OM, and I.

\textit{(Sharon's comments: You don't need to
  describe why we include a planet in EOD -- this is covered at the
  beginning of Section~\ref{sec:update} as we discuss the `scope of
  EOD'. Just say what this flag is. Also, right now it includes RV,
  Transit, and also some Timing planets. The first sentence sounds
  like as long as a planet is discovered via RV and transit, it'll be
  in EOD, which is not true, I think.)}

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
ING, IMAGING, TIMING and ASTROMETRY fields for planets detected by
methods other than radial velocity and transit. Since planets detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org. However, if planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have EOD flags. See Section~\ref{sec:kepler} for more information about `Other Planets'.

\textit{(Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.)}

@@

DIST: actually, DIST is not added since Wright 2011 (It was just left out)
We report distance of the host star in the unit of pc.

@@

We now report the month when the peer-reviewed paper is accepted to ApJ to better track of the trend in exoplanetary detections. Moreover, we report the discovery methods for the host star and the planet separately: STARDISCMETH and PLANETDISCMETH. See Section~ for more details.

@@

DISCMETH - We have replaced DISCMETH with PLANETDISCMETH and STARDISCMETH to better report how the host star and the planet are detected.
